\documentclass[a4paper,11pt]{article}
 
% --- Packages
\usepackage{booktabs}
\usepackage[margin=1.5cm]{caption}
\usepackage{float}
\usepackage[table,xcdraw]{xcolor}
\usepackage{graphicx}
\usepackage{amsfonts,amsthm,amsmath,mathtools,graphicx,geometry}
\usepackage{enumitem} 
\usepackage{multicol}
\DeclareMathOperator*{\argmin}{arg\,min}

% --- Custom commands
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\red}[1]{\textcolor{red}{#1}}
%% define command for averaging operator
\newcommand{\chevron}[1]{\left\langle #1 \right\rangle}
\newcommand{\pderiv}[3][]{% \pderiv[<order>]{<func>}{<var>} 
  \ensuremath{\frac{\partial^{#1} {#2}}{\partial {#3}^{#1}}}}
\newcommand{\noi}{\noindent}
\newcommand{\ep}{\epsilon} 
\newcommand{\pr}{\partial}
% --- Formatting 
\geometry{margin=1in}
\title{\vspace{-4ex}RANS Modeling in a Channel}
\author{Gopal Yalla, Clark Pederson, Tim Smith, Sean Carney}
\date{\today}

\pdfinfo{%
  /Title    (RANS Modeling in a Channel)
  /Author   (Gopal Yalla, Clark Pederson, Tim Smith, Sean Carney)
}
\graphicspath{ {figs/} }
\DeclareGraphicsExtensions{.png}

\begin{document}
\maketitle
\section{Developing the channel flow equations}

We begin by developing the $k-\epsilon$ model for channel flow with Durbin's
$\chevron{v^2}-f$ formulation of the eddy viscosity near
the wall. We chose this wall treatment since it fundamentally
addresses the fact that near the wall, the eddy viscosity is a function of the
wall normal velocity. Out of the models which we have been introduced to, this
formulation seems to be the best tradeoff between complexity and theoretical
backing for anisotropy near the wall.    

The unsteady incompressible Reynolds averaged Navier-Stokes equations, 
$k-\epsilon$, and $\chevron{v^2}-f$ model equations are as follows:

\begin{align}
\pderiv{U_i}{x_i} &= 0 \label{eq:continuity} \\
\pderiv{U_i}{t} + U_j\pderiv{U_i}{x_j} &= -\pderiv{P}{x_i} +
\pderiv{}{x_j}\left(\nu\pderiv{U_i}{x_j} - \chevron{u_i u_j}\right) \\
\pderiv{k}{t} + U_j\pderiv{k}{x_j} &= -r_{ij}\pderiv{U_i}{x_j} - \epsilon +
\pderiv{}{x_j}\left(\frac{\nu_T}{\sigma_k}\pderiv{k}{x_j}\right) +
\nu\frac{\partial^2 k}{\partial x_j \partial x_j} \\
\pderiv{\epsilon}{t} + U_j\pderiv{\epsilon}{x_j} &=
-\frac{1}{T}\left(C_{\epsilon 1} \mathcal{P} + C_{\epsilon 2} \epsilon\right) +
\pderiv{}{x_j}\left(\frac{\nu_T}{\sigma_\epsilon}\pderiv{\epsilon}{x_j}\right) +
\nu\frac{\partial^2 \epsilon}{\partial x_j \partial x_j} \\
\pderiv{\chevron{v^2}}{t} + U_j\pderiv{\chevron{v^2}}{x_j} &= kf +
\pderiv{}{x_j}\left((\nu_T+\nu)\pderiv{\chevron{v^2}}{x_j}\right) - \epsilon
\frac{\chevron{v^2}}{k} \\
L^2 \nabla^2 f - f &= -C_2 \frac{\mathcal{P}}{k} + \frac{C_1}{T} \left(
\frac{\chevron{v^2}}{k} - \frac{2}{3} \right) 
%r_{ij} &= -\nu_T \left(\pderiv{U_i}{x_j} + \pderiv{U_j}{x_i}\right) + \frac{2
%k}{3}\delta_{ij} \\ 
%\nu_T &= \frac{3}{2}C_\mu\chevron{v^2}T 
\label{eq:redistribution}
\end{align}

\noi where 

\begin{align*}
\nu_T &= \frac{3}{2}C_\mu \chevron{v^2} T \\
\mathcal{P} &= \nu_T\left( \pderiv{U_j}{x_i} + \pderiv{U_i}{x_j}\right)\pderiv{U_j}{x_i} \\
T &= \max \left\{ \frac{k}{\ep} , 6 \left( \frac{v}{\ep} \right)^{\frac{1}{2}}
\right\} \\
L &= \max \left\{ C_L \frac{k^{3/2}}{\ep}, C_\eta \left( \frac{v^3}{\ep}
\right)^{1/4} \right\}
\end{align*}

We consider channel flow through a rectangular duct of height $h= 2\delta$, with
the bottom and top walls at $y=0$ and $y=2\delta$, and the midplane at
$y=\delta$.
Here we are modeling ``fully developed'' channel flow in the streamwise, $x$,
direction such that statistics do not change in the spanwise, $z$, or
streamwise directions. As in Pope \cite{pope} we neglect the mean spanwise
velocity. 
We enforce the no slip condition at the boundary, so that
$U_i=u_i=0 \, \forall i$. Since at the wall
$\pderiv{U}{x}=\pderiv{W}{z} = 0$, continuity implies that
$\pderiv{V}{y}=0$ and thus $V=0$ everywhere. Moreover, the flow is statistically
symmetric about the mid-plane $y = \delta$. These assumptions and conditions
imply that the original system, Eqns.
(\ref{eq:continuity})-(\ref{eq:redistribution}), is simplified to: 

\begin{align}
	\label{eq:ssv2f1}
        \pderiv{U}{t} &= -\pderiv{P}{x} +
\pderiv{}{y}\left((\nu+\nu_T)\pderiv{U}{y}\right) \\
        \pderiv{k}{t} &= \nu_T\left(\pderiv{U}{y}\right)^2 + 
\pderiv{}{y}\left((\nu+\frac{\nu_T}{\sigma_k})\pderiv{k}{y}\right) \\
        \pderiv{\ep}{t} &= \frac{1}{T}\left(C_{\ep
1}\nu_T\left(\pderiv{U}{y}\right)^2 - C_{\ep 2}\ep\right) + 
\pderiv{}{y}\left((\nu+\frac{\nu_T}{\sigma_\ep})\pderiv{\ep}{y}\right) \\
        \pderiv{\chevron{v^2}}{t} &= kf - \frac{1}{T}\chevron{v^2} +
\pderiv{}{y}\left((\nu+\nu_T)\pderiv{\chevron{v}}{y}\right) \\
        0 &= \left( L^2\nabla^2 - I\right)f +
C_2\frac{\nu_T}{k}\left(\pderiv{U}{y}\right)^2 -
\frac{C_1}{T}\left(\frac{\chevron{v^2}}{k}-\frac{2}{3}\right)
	\label{eq:ssv2f5}
\end{align}

The constants are defined as follows: 
\begin{multicols}{2}
\begin{enumerate}
	\item $C_\mu = 0.09$
        \item $C_k = 1.0$
	\item $\sigma_\ep = 1.3$
	\item $C_2 = 0.4$	
\end{enumerate}
\columnbreak 

\begin{itemize}
	\item[5.] $C_1 = 0.3$
	\item[6.] $C_{\ep 1} = 1.4[1 + 0.045 \sqrt{k/\chevron{v^2}}]$
	\item[7.] $C_{\ep 2} = 1.92$  
	\item[8.] $C_\eta = 16$
	\item[9.] $C_L = 0.2$
\end{itemize}
\end{multicols}

\section{Non-Uniform Grid}
In order to reduce the computational requirements, a non-uniform spacing of points was used.  This allows a fine resolution near the wall, where the resolution must be on the order of the wall-units, and a coarse resolution in the center of the channel.  A set of uniform points, $\chi$, was defined such that $\chi=0$ corresponds to the channel wall and $\chi=1$ corresponds to the centerline.  This set of uniform points was remapped to the nonuniform mesh, $\tilde{y} = y/\delta$, using the mapping function used by Lee and Moser \cite{Lee},
\begin{equation} \label{eq:mapping}
 \frac{y}{\delta} = \frac{\sin(\eta (\chi-1) \pi/2)}{\sin(\eta \pi/2)}+1, \quad 0 \le \chi \le 1
\end{equation}
where $\eta$ is an adjustable parameter that controls the resolution near the wall. When $\eta$ is equal to 1, the wall-spacing is finest.  When $\eta$ is very small, the mesh is approximately uniform.  For our simulation, we use $\eta = 0.97$.  Using a value other than $\eta = \pm 1$ prevents the derivative of $y$ with respect to $\chi$ from going to zero at the walls.

The formula in Eq. \ref{eq:mapping} can be simplified by defining a few constants based on $\eta$:
\begin{equation}
 \frac{y}{\delta} = \frac{\sin\big((\chi-1)a\big)}{b}+1, \quad 0 \le \chi \le 1
\end{equation}
where $a = \eta \pi/2$ and $b = \sin (\eta \pi/2)$.

The inverse mapping and its derivatives can be written as:
\begin{align}
  \chi &= \frac{\sin^{-1}(by-b)}{a} + 1 \\
  \frac{\mathrm{d}\chi}{\mathrm{d}\tilde{y}} &= \frac{b}{a \sqrt{1-b^2(y-1)^2}} \label{eq:chi-y-1} \\
  \frac{\mathrm{d}^2\chi}{\mathrm{d}\tilde{y}^2} &= \frac{b^2(by-b)}{a\big(1-(b-by)^2\big)^{3/2}} \label{eq:chi-y-2}
\end{align}
where $a$ is a constant equal to the denominator in Eq. \ref{eq:mapping}.  Using the chain rule, the derivatives of a variable $\phi$ on the nonuniform grid, $\tilde{y}$ can be computed using derivatives on the uniform grid, $\chi$ as follows:
\begin{align}
 \pderiv{\phi}{\tilde{y}} &= \frac{\mathrm{d}\chi}{\mathrm{d}\tilde{y}} \pderiv{\phi}{\chi} \label{eq:phi-y-1} \\
 \pderiv[2]{\phi}{\tilde{y}} &= \frac{\mathrm{d}^2\chi}{\mathrm{d}\tilde{y}^2} \pderiv{\phi}{\chi} + \Big(\frac{\mathrm{d}\chi}{\mathrm{d}\tilde{y}} \Big)^2 \pderiv[2]{\phi}{\chi}  \label{eq:phi-y-2} 
\end{align}
In order to acheive a near-wall resolution on the order of $\Delta y ~ \delta_v$, the distance between the first two grid points must be $\delta_v$.  This leads to the equation:
\begin{equation}
 \Delta \chi = \frac{\sin^{-1}(b\delta_v -b)}{a}+1
\end{equation}

If we use $\delta = 1$ as our channel width, then $y = \tilde{y}$ and $\delta_v = 1/\mathrm{Re}_{\tau}$.  This leads to an equation for the required number of grid points, $n$, as:
\begin{equation}
 n = \frac{a}{\sin^{-1}(b/\mathrm{Re}_{\tau}-b)+a}
\end{equation}
Using a value of $\eta = .97$ for the mapping parameter, the number of points required for $\mathrm{Re}_{\tau}=5200$ and $\mathrm{Re}_{\tau}=10000$ is 390 and 735 respectively. This is significantly lower than the uniform grid sizes of 5,200 and 10,000.





\clearpage
\begin{thebibliography}{3}
\bibitem{Lee}
Lee, Myoungkyu and R.D. Moser, ``Direct numerical simulation of turbulent channel flow up to $\mathrm{Re}_{\tau}=5200$,'' J. Fluid Mech. 774 (2015) 395–415. doi:10.1017/jfm.2015.268.
\bibitem{Durbin}
    Durbin, Paul A., and BA Pettersson Reif. \textit{Statistical theory and
modeling for turbulent flows}. John Wiley \& Sons, 2011.
\bibitem{pope}
        Pope, Stephen B. \textit{Turbulent flows}. (2001): 2020.
 
\newpage



\end{thebibliography}


\end{document}
